% =============================================================================
% methods_formula_patches.tex
%
% Patch bundle for `methods_draft.tex` — fills the formula gaps and adds a
% Pt(Au) extension note.
%
% FRAMING (revised 2026-05-13 evening per user direction): the Methods main
% body is written for the principal test system Al(Mg) (the only system for
% which the full HMC + (T, X_c) grid has been run end-to-end as of this
% report). The atomistic-stage methodology (Voronoi → anneal → a-CNA → ΔE
% spectrum → Wagih spectrum validation) has additionally been applied to
% Pt(Au), but the Pt(Au) HMC stage is still in progress (collaborator's
% portion). PATCH 11 captures this asymmetry explicitly as a "system
% extension" subsection so the report can honestly state what has and has
% not been done for the second alloy.
%
% Each PATCH below is a self-contained LaTeX block; paste-location is stated
% at the top of each block.
% =============================================================================


% =============================================================================
% PATCH 0a — Intro paragraph (revised)
% PASTE: at the very top of \section{Methodology}, REPLACING the existing
%        first paragraph.
% =============================================================================

Our objective is to test where the independent-site Fermi--Dirac (FD)
framework of Wagih \emph{et al.}~\cite{Wagih2020} for grain-boundary (GB)
solute segregation breaks down in $(T, X_c)$ space, where $T$ is the
temperature and $X_c$ the global solute fraction. The methodology is
structured as a hypothesis-versus-ground-truth comparison on a single
shared atomistic basis (Fig.~\ref{fig:method}): the FD framework
provides the prediction $X_\mathrm{GB}^\mathrm{FD}(T, X_c)$, hybrid
Monte Carlo / molecular dynamics (HMC) sampling provides the ground
truth $X_\mathrm{GB}^\mathrm{HMC}(T, X_c)$, and the gap between them
is the testable quantity. The principal test system in this report
is Al(Mg); a parallel sub-study on Pt(Au) has so far completed the
atomistic and spectrum-validation stages and is described in
Sec.~\ref{sec:meth:ptau}. Both systems' atomistic parameters are
tabulated in Table~\ref{tab:systems}. The equations and the HMC
algorithm are stated in Apps.~\ref{app:eq}--\ref{app:alg}.


% =============================================================================
% PATCH 0b — Systems-studied table
% PASTE: immediately after PATCH 0a's paragraph, before
%        \subsection{Atomistic base...}. Stage column makes the asymmetry
%        between the two systems explicit.
% =============================================================================

\begin{table}[t]
\centering
\caption{Atomistic systems used in this report. Both are FCC hosts with
a dilute substitutional solute, processed by the same generic
polycrystal-build / anneal / GB-ID / $\Delta E$-spectrum pipeline.
Al(Mg) is the principal test system and has been driven through the
full pipeline including HMC on the $(T, X_c)$ grid
(Sec.~\ref{sec:meth:grid}); Pt(Au) is a parallel sub-study that has
so far completed the atomistic and spectrum-validation stages only,
with its HMC sampling currently in progress
(Sec.~\ref{sec:meth:ptau}). The $f_\mathrm{GB}$ asymmetry is
geometric: smaller boxes have higher surface-to-volume ratios, so
Pt(Au)'s higher value reflects its smaller box edge rather than an
intrinsic material property.}
\label{tab:systems}
\begin{tabular}{lcc}
\toprule
                                          & Al(Mg)                            & Pt(Au)                          \\
\midrule
host                                      & Al                                & Pt                              \\
solute                                    & Mg                                & Au                              \\
EAM potential                             & Mendelev 2009~\cite{Mendelev2009} & O'Brien 2017~\cite{OBrien2017}  \\
\quad LAMMPS \texttt{pair\_style}         & \texttt{eam/fs}                   & \texttt{eam/alloy}              \\
lattice constant $a$ (\AA)                & 4.05                              & 3.98                            \\
host bulk modulus $K$ (GPa)               & 76                                & 280                             \\
box edge $L$ (\AA)                        & 200                               & 100                             \\
total atoms $N_\mathrm{tot}$              & 475{,}715                         & 62{,}096                        \\
grain seeds $N_\mathrm{grains}$           & 16                                & 8                               \\
GB atoms $N_\mathrm{GB}$ (post-anneal)    & 89{,}042                          & 23{,}272                        \\
GB fraction $f_\mathrm{GB}$               & 0.187                             & 0.375                           \\
host melting $T_\mathrm{melt}$ (K)        & 933                               & 2041                            \\
anneal hold $T_\mathrm{hold}$ (K)         & 373                               & 816                             \\
$\Delta E_i$ spectrum sample $n$          & 500                               & 500                             \\
\bottomrule
\end{tabular}
\end{table}


% =============================================================================
% PATCH 1 — ΔE simplification note (Al/Mg-concrete)
% PASTE: in app:eq, immediately AFTER the existing equation eq:dE.
% =============================================================================

For the pure-Al polycrystal base used in this work,
$E^{\mathrm{bulk-Al}} = E_i^{\mathrm{GB-Al}} = E_\mathrm{pure}$ — both
equal the total energy of the un-substituted polycrystal — and
Eq.~(\ref{eq:dE}) simplifies to the operational two-point form
\begin{equation}\label{eq:dE_op}
\Delta E_i \;=\; E_i^{\mathrm{GB-Mg}}
            \;-\; \big\langle E^{\mathrm{bulk-Mg}} \big\rangle
\qquad (\text{pure-Al host}),
\end{equation}
in which $E_i^{\mathrm{GB-Mg}}$ is the total potential energy of the
polycrystal after a single Al $\to$ Mg substitution at GB site $i$
followed by conjugate-gradient minimisation with tight tolerances
$\mathrm{etol} = \mathrm{ftol} = 10^{-25}$ (matching
Ref.~\cite{Wagih2020}'s \texttt{calculate\_E\_GB\_solute.in} protocol),
and $\langle E^{\mathrm{bulk-Mg}} \rangle$ is the same total energy
averaged over $n_\mathrm{ref} = 10$ well-separated bulk-Al reference
positions. The sign convention follows Wagih: $\Delta E_i < 0$ means
GB site $i$ is energetically favourable for Mg (segregating); $\Delta
E_i > 0$ disfavoured. Eq.~(\ref{eq:dE_op}) is what
\texttt{scripts/sample\_delta\_e.py} evaluates per GB site; the bulk
reference scatter ($\sigma_{E^{\mathrm{bulk-Mg}}} = 8.1$~meV) is one
to two orders of magnitude below typical per-site signal magnitudes
($|\Delta E_i| \sim 100$--$500$~meV). For the Pt(Au) system the
analogous formula holds with Al $\to$ Pt and Mg $\to$ Au throughout
(Sec.~\ref{sec:meth:ptau}; $\sigma_{E^{\mathrm{bulk-Au}}}
= 5.3$~meV).


% =============================================================================
% PATCH 2 — X_GB(t) definition
% PASTE: in app:eq, after the canonical FD equation eq:FD_canon.
% =============================================================================

\paragraph*{HMC observable.}
The instantaneous GB Mg fraction at production time $t$ is
\begin{equation}\label{eq:Xgb_def}
X_\mathrm{GB}(t) \;\equiv\; \frac{1}{N_\mathrm{GB}}
\sum_{i \in \mathrm{GB}}
\mathbb{1}\!\big\{\, \text{site $i$ is occupied by Mg at time $t$} \,\big\} ,
\end{equation}
where $\mathbb{1}\{\cdot\}$ is the indicator function and the sum is
over the $N_\mathrm{GB}$ atoms tagged as GB by the a-CNA mask
(App.~\ref{app:atomistic}). The reported HMC observable is the
post-burn-in time average $\langle X_\mathrm{GB}\rangle_t$ together
with the stationary block-bootstrap 95\% confidence interval
defined in Sec.~\ref{sec:meth:stats}, Eq.~(\ref{eq:block_bootstrap}).


% =============================================================================
% PATCH 3 — Energy units and closed-box ceiling
% PASTE: in app:eq, at the top (before the substantive equations).
% =============================================================================

\paragraph*{Energy units.}
LAMMPS evaluates total energies in eV (metal units). All $\Delta E_i$
histograms, fits, and figures throughout this work are reported in
kJ/mol via the standard conversion
\begin{equation}\label{eq:unit_kjmol}
\Delta E \;[\mathrm{kJ/mol}]
\;=\; \frac{e \cdot N_A}{1000} \, \Delta E \;[\mathrm{eV}]
\;=\; 96.485 \, \Delta E \;[\mathrm{eV}] ,
\end{equation}
where $e = 1.602 \times 10^{-19}$~C is the elementary charge and
$N_A = 6.022 \times 10^{23}\,\mathrm{mol}^{-1}$ is Avogadro's number
(the factor $10^{-3}$ converts J/mol to kJ/mol).

\paragraph*{Closed-box ceiling on $X_\mathrm{GB}$.}
A closed simulation cell with global Mg fraction $X_c$ has a hard
upper bound on $X_\mathrm{GB}$ set by mass conservation alone — the
configuration in which every Mg atom sits at a GB site:
\begin{equation}\label{eq:ceiling}
X_\mathrm{GB}^{\mathrm{ceil}}(X_c) \;=\; X_c \, N_\mathrm{tot} / N_\mathrm{GB}
\;=\; X_c / f_\mathrm{GB} .
\end{equation}
Both $X_\mathrm{GB}^{\mathrm{HMC}}$ and $X_\mathrm{GB}^{\mathrm{FD,canon}}$
are bounded above by Eq.~(\ref{eq:ceiling}); the ceiling line is
plotted alongside HMC and FD curves in the headline panel of the
Results.


% =============================================================================
% PATCH 4 — Voronoi region (replaces the inline "3D Voronoi tessellation..."
%           in app:atomistic).
% =============================================================================

\paragraph*{Voronoi tessellation.}
Given $N_\mathrm{grains}$ seed positions
$\{\mathbf{s}_k\}_{k=1}^{N_\mathrm{grains}}$ drawn uniformly inside the
periodic $L^3$ box, the grain assigned to each candidate FCC lattice
site $\mathbf{r}$ is
\begin{equation}\label{eq:voronoi}
k(\mathbf{r}) \;=\; \arg\min_{1 \le k \le N_\mathrm{grains}}
\big\| \mathbf{r} - \mathbf{s}_k \big\|_\mathrm{PBC} ,
\end{equation}
where $\|\cdot\|_\mathrm{PBC}$ is the minimum-image Euclidean distance
under periodic boundary conditions, implemented via a $k$-d tree
nearest-neighbour lookup. Each grain receives a uniformly random
$\mathrm{SO}(3)$ orientation (Haar measure on rotation matrices) before
its FCC lattice is rotated into place. Lattice sites whose nearest
inter-grain distance is below the close-pair cutoff
$r_\mathrm{cut} = a/(2\sqrt{2})$ (one half the FCC nearest-neighbour
spacing) are pruned to prevent unphysically close atomic pairs at
the as-built GBs; the resulting deficit is $\sim 2\%$ of the ideal
FCC atom count.


% =============================================================================
% PATCH 5 — Anneal thermostat / barostat schedule
% PASTE: in app:atomistic, replacing or supplementing the existing inline
%        "anneal schedule follows Wagih..." description.
% =============================================================================

\paragraph*{Anneal schedule.}
The five-stage decomposition and the choice $T_\mathrm{hold} = 0.4
T_\mathrm{melt}$ (Table~\ref{tab:systems}) follow Wagih~\cite{Wagih2020};
the explicit damping constants, CG tolerances, and the 3 K/ps cool
rate below are project-specific choices that reproduce Wagih's
end-state to within the bulk reference scatter of
Eq.~(\ref{eq:dE_op}).
\begin{enumerate}\itemsep0pt\parsep0pt\setlength{\leftmargin}{0pt}
\item Conjugate-gradient minimisation to absorb residual close-pair strain from the Voronoi construction (\texttt{etol} / \texttt{ftol} $= 10^{-6} / 10^{-8}$~eV / (eV/\AA), max iterations $5000$).
\item NVT temperature ramp from 1~K to $T_\mathrm{hold}$ over 5~ps using a Nos\'e--Hoover thermostat with damping $\tau_T = 100$~fs.
\item NPT hold at $T_\mathrm{hold}$ for 250~ps with isotropic Nos\'e--Hoover thermo-barostat ($\tau_T = 100$~fs, $\tau_P = 1000$~fs, target $P = 0$) to relax GB structure.
\item NPT cool from $T_\mathrm{hold}$ to 1~K at $3$~K/ps with the same barostat settings.
\item Final zero-pressure box relaxation by conjugate gradient (\texttt{fix box/relax}, \texttt{iso 0.0}, tolerances $10^{-8} / 10^{-10}$).
\end{enumerate}
The annealed configuration is the fixed substrate for all subsequent
measurements.


% =============================================================================
% PATCH 6 — Skew-normal PDF and moment-to-parameter relations
% PASTE: in app:dE_compare, at the top of the appendix (before the n=500
%        justification paragraph that already exists).
% =============================================================================

\paragraph*{Skew-normal fit.}
The $\Delta E_i$ spectrum is fit by the three-parameter skew-normal
PDF~\cite{Azzalini1985} (the same form used by Wagih's
SI~\cite{Wagih2020}):
\begin{equation}\label{eq:skewnorm}
f(\Delta E; \mu, \sigma, \alpha)
\;=\; \frac{2}{\sigma} \, \varphi\!\left(\tfrac{\Delta E - \mu}{\sigma}\right)
\, \Phi\!\left(\alpha \, \tfrac{\Delta E - \mu}{\sigma}\right),
\end{equation}
where $\varphi$ and $\Phi$ are the standard-normal PDF and CDF.
$\mu$ is the location parameter, $\sigma > 0$ the scale parameter,
and $\alpha$ the shape (skewness) parameter; $\alpha = 0$ recovers
the symmetric Gaussian. Parameters are obtained by maximum likelihood
(\texttt{scipy.stats.skewnorm.fit}). The sample mean and standard
deviation are NOT $\mu$ and $\sigma$ when $\alpha \neq 0$:
\begin{equation}\label{eq:skewnorm_moments}
\langle \Delta E \rangle = \mu + \sigma \delta \sqrt{2/\pi},
\qquad
\mathrm{var}(\Delta E)  = \sigma^2 \!\left(1 - \tfrac{2 \delta^2}{\pi}\right),
\qquad
\delta = \alpha / \sqrt{1+\alpha^2}.
\end{equation}
Fit parameters are reported in kJ/mol via Eq.~(\ref{eq:unit_kjmol})
and matched against Wagih's SI tables for each alloy.


% =============================================================================
% PATCH 7 — Two-sample Kolmogorov–Smirnov
% PASTE: in app:dE_compare, after PATCH 6.
% =============================================================================

\paragraph*{Spectrum-level comparison: two-sample Kolmogorov--Smirnov.}
Let $\hat F_1, \hat F_2$ denote the empirical CDFs of two $\Delta E$
samples of sizes $n_1, n_2$. The two-sample Kolmogorov--Smirnov
statistic and asymptotic two-sided $p$-value are
\begin{equation}\label{eq:KS}
D \;=\; \sup_{\Delta E} \big|\, \hat F_1(\Delta E) - \hat F_2(\Delta E) \,\big|,
\qquad
p \;=\; 2 \sum_{k=1}^{\infty} (-1)^{k-1} \exp(-2 k^2 \lambda^2),
\quad
\lambda = D \sqrt{\tfrac{n_1 n_2}{n_1 + n_2}},
\end{equation}
implemented in \texttt{scipy.stats.ks\_2samp}. We report
$(D, p)$ for our $n_1 = 500$ Al(Mg) spectrum versus the Wagih Zenodo
reference ($n_2 = 82{,}646$). The KS $p$-value alone is
sample-size-asymmetric: at $n_1 \ll n_2$ a small $p$ can reflect
tail under-sampling on the small-$n$ side rather than a real
distribution mismatch — a regime that does not affect the Al(Mg)
comparison ($p = 0.89$) but does affect the Pt(Au) comparison
($p = 6\times 10^{-4}$, Sec.~\ref{sec:meth:ptau}). The
fit-parameter bootstrap CI of Eq.~(\ref{eq:fit_bootstrap}) below is
introduced as the complementary metric robust to this regime.


% =============================================================================
% PATCH 8 — a-CNA GB identification (replaces the existing one-liner in
%           app:atomistic).
% =============================================================================

\paragraph*{GB identification.}
The annealed configuration is classified atom-by-atom using adaptive
common-neighbour analysis (a-CNA)~\cite{Stukowski2012}, which assigns
each atom one of $\{\text{FCC}, \text{BCC}, \text{HCP}, \text{ICO},
\text{other}\}$ based on the topology of its $12$ nearest neighbours.
The cutoff radius for the neighbour set is determined adaptively per
atom, avoiding fixed-cutoff failures near distorted regions. Atoms
not classified as FCC (the bulk lattice phase) are designated
\emph{GB atoms}. The resulting binary mask of $N_\mathrm{GB}$ sites
(Table~\ref{tab:systems}) is generated once on the annealed polycrystal
and held fixed across all downstream measurements — the $\Delta E$
sampling, the FD predictor [via $f_\mathrm{GB}$ in
Eq.~(\ref{eq:ceiling}) and the summand of Eq.~(\ref{eq:FD_canon})],
and the HMC observable (Eq.~\ref{eq:Xgb_def}).


% =============================================================================
% PATCH 9 — Stationary block bootstrap CI on ⟨X_GB⟩
% PASTE: in sec:meth:stats, replacing the existing one-sentence description.
% =============================================================================

\paragraph*{Trajectory-level CI on $\langle X_\mathrm{GB}\rangle_t$.}
Let $\{x_t\}_{t=1}^{n}$ be the post-burn-in $X_\mathrm{GB}(t)$ frames
sampled at 1~ps spacing (the first 20\% of frames are dropped as
burn-in; $n \approx 240$ for our default 300~ps production). We
compute the 95\% CI on $\langle X_\mathrm{GB}\rangle_t$ via the moving
block bootstrap of K\"unsch~\cite{Kunsch1989}: at each of $B = 2000$
replicates, $n_b = \lfloor n / L_b \rfloor$ overlapping blocks of fixed
length $L_b = 5$ frames are drawn uniformly at random (with
replacement) from $\{x_t\}$ and concatenated into a replicate series
$\{x_t^{(b)}\}_{t=1}^{n_b L_b}$, whose mean $\bar x^{(b)}$ is recorded.
The 95\% CI is the empirical $[2.5, 97.5]$ percentile range of
$\{\bar x^{(b)}\}_{b=1}^{B}$:
\begin{equation}\label{eq:block_bootstrap}
\mathrm{CI}_{95\%}\!\left(\langle X_\mathrm{GB}\rangle_t\right)
\;=\; \Big[\, q_{2.5}\!\left(\{\bar x^{(b)}\}\right), \;
              q_{97.5}\!\left(\{\bar x^{(b)}\}\right) \,\Big].
\end{equation}
The block length $L_b = 5$~frames is approximately twice the
integrated autocorrelation time of $X_\mathrm{GB}(t)$ under the swap
schedule of Algorithm~\ref{alg:hmc}. For trajectories too short to
support the block bootstrap ($n < 2 L_b$), the CI falls back to the
Wald approximation $\bar x \pm 1.96 \, s_{\bar x}$ with
$s_{\bar x} = s/\sqrt{n}$ — a regime not entered by any of the
runs reported in this work.


% =============================================================================
% PATCH 10 — Fit-parameter bootstrap CI (introduced for Pt(Au); applies to
%             any (n_1, n_2) where n_1 << n_2).
% PASTE: in app:dE_compare, after PATCH 7.
% =============================================================================

\paragraph*{Fit-parameter bootstrap CI.}
When the Wagih reference contains $n_2 \gg n_1$ sites
[Eq.~(\ref{eq:KS})], the KS $p$-value becomes acutely sensitive to
small tail offsets that any random $n_1$-sized sub-sample of the
larger pool also exhibits. As a complementary spectrum-validation
test we therefore build the bootstrap distribution of the fit
parameters $\{\mu, \sigma, \alpha\}$ that one would obtain from
random $n_1$-sized sub-samples of the Wagih pool. Concretely:
\begin{enumerate}\itemsep0pt\parsep0pt
\item Draw $B = 10{,}000$ resamples
      $\{\Delta E_j^{(b)}\}_{j=1}^{n_1}$ with replacement from the
      Wagih reference pool of size $n_2$.
\item Fit each resample to Eq.~(\ref{eq:skewnorm}), yielding
      $\big(\mu^{(b)}, \sigma^{(b)}, \alpha^{(b)}\big)$.
\item Form the 95\% percentile CI in each parameter:
\begin{equation}\label{eq:fit_bootstrap}
\mathrm{CI}_{95\%}(\theta) \;=\; \Big[\, q_{2.5}\!\left(\{\theta^{(b)}\}_{b=1}^{B}\right), \;
                                              q_{97.5}\!\left(\{\theta^{(b)}\}_{b=1}^{B}\right) \,\Big],
\quad \theta \in \{\mu, \sigma, \alpha\}.
\end{equation}
\end{enumerate}
The measurement is declared statistically consistent with the Wagih
reference if its maximum-likelihood
$(\hat\mu, \hat\sigma, \hat\alpha)$ all fall inside their bootstrap
CI95. This criterion was introduced for the Pt(Au) sub-study where
the $n_1 \ll n_2$ regime makes raw-KS unreliable
(Sec.~\ref{sec:meth:ptau}); for the Al(Mg) primary system where
$p_\mathrm{KS} = 0.89$ already passes, the bootstrap CI is reported
alongside as confirmation.


% =============================================================================
% PATCH 11 — Pt(Au) system extension subsection
% PASTE: as a NEW subsection at the END of \section{Methodology}, after
%        \subsection{Statistical analysis} and BEFORE the method figure
%        (Fig.~\ref{fig:method}). Suggested label: sec:meth:ptau.
% =============================================================================

\subsection{Extension to a second alloy: Pt(Au)}\label{sec:meth:ptau}

Subsections~\ref{sec:meth:base}--\ref{sec:meth:stats} describe the
methodology for the principal test system Al(Mg). A parallel sub-study
on Pt(Au) is in progress as a second alloy data point on the same
hypothesis. As of this report's writing, Pt(Au) has been driven
through the atomistic build, anneal, GB identification, $\Delta E_i$
spectrum sampling, and Wagih-reference spectrum validation; the
$(T, X_c)$ HMC grid is currently being acquired by the collaborator
and its results will be reported separately. We document below what
methodology is shared with the Al(Mg) main line and what differs.

\paragraph*{Shared methodology.}
The polycrystal construction [Eq.~(\ref{eq:voronoi})], anneal schedule
(App.~\ref{app:atomistic}), a-CNA GB identification, per-site
$\Delta E_i$ sampling [Eqs.~(\ref{eq:dE}), (\ref{eq:dE_op})], the
skew-normal fit [Eq.~(\ref{eq:skewnorm})], and the two spectrum-level
validation tests against Wagih [the KS statistic of
Eq.~(\ref{eq:KS}) and the fit-parameter bootstrap CI of
Eq.~(\ref{eq:fit_bootstrap})] are executed by the same Python /
LAMMPS scripts for both systems. Where the Pt(Au) input parameters
differ from Al(Mg), the system-specific values are taken from
Table~\ref{tab:systems}; the analogous $\Delta E$ formula for Pt(Au)
is obtained from Eq.~(\ref{eq:dE_op}) by replacing Al $\to$ Pt and
Mg $\to$ Au throughout.

\paragraph*{System-specific differences (Pt(Au)).}
\begin{enumerate}\itemsep0pt\parsep0pt
\item \emph{EAM file format.} Pt(Au) uses O'Brien et al.\
   2017~\cite{OBrien2017} in standard \texttt{eam/alloy} (Daw--Baskes
   setfl); Al(Mg) uses Mendelev 2009 in Finnis--Sinclair
   \texttt{eam/fs}. The two are equivalent EAM embedding + pair forms
   reading per-element vs per-element-pair density tabulations;
   alloy-agnostic at the $\Delta E$-sampling driver level via
   a single CLI flag.
\item \emph{Smaller production box: 100$^3$\,\AA$^3$ for Pt(Au) vs
   200$^3$\,\AA$^3$ for Al(Mg).} The Pt EAM has roughly $3.7\times$
   the bulk modulus of the Al EAM, which scales the per-site CG
   iteration count needed to hit $\mathrm{etol} = 10^{-25}$;
   empirically $\sim 5\times$ slower per site than Al(Mg). The
   Pt(Au) box is therefore reduced from 200~\AA{} to 100~\AA{} to
   keep $n = 500$ spectrum sampling within the same SLURM wall-time
   budget. The trade-off is a larger geometric $f_\mathrm{GB} =
   0.375$ vs $0.187$ for Al(Mg) (smaller box, higher
   surface-to-volume ratio). The spectrum-validation tests of
   Eqs.~(\ref{eq:KS}) and (\ref{eq:fit_bootstrap}) compare per-site
   $\{\Delta E_i\}$ distributions, not aggregate occupancies, so the
   $f_\mathrm{GB}$ asymmetry does not bias them.
\item \emph{Hold temperature.} $T_\mathrm{hold} = 0.4 T_\mathrm{melt}
   = 816$~K for Pt(Au) (vs 373~K for Al(Mg)), preserving Wagih's
   protocol scale.
\item \emph{Wagih reference dataset format.} The Pt(Au) reference is
   distributed as a single per-site \texttt{seg\_kJ\_per\_mol} column
   in the Zenodo \texttt{accelerated\_model} dump; the Al(Mg)
   reference is a paired (\texttt{seg\_energies.txt},
   \texttt{bulk\_solute.dat}) text format. The Pt(Au) comparison
   driver uses a dump-column reader; the Al(Mg) driver uses a
   text-pair reader; both produce $(D, p)$ via Eq.~(\ref{eq:KS}).
\end{enumerate}

\paragraph*{Pt(Au) spectrum-validation outcome.}
The Pt(Au) $\Delta E_i$ spectrum from $n_1 = 500$ randomly chosen GB
sites yields skew-normal fit $(\hat\mu, \hat\sigma, \hat\alpha) =
(+3.16, 10.31, -1.16)$~kJ/mol. All three parameters fall inside the
$B = 10{,}000$ bootstrap 95\% CI computed by sub-sampling
$n_1 = 500$ from Wagih's $n_2 = 97{,}440$-site reference pool, with
standardised deviations $|z| \le 1.6$ on each
[Eq.~(\ref{eq:fit_bootstrap})]. The raw KS test yields $D = 0.090$,
$p = 6.2 \times 10^{-4}$, which formally rejects identity at the
$p > 0.5$ project bar but is driven by the $n_1 \ll n_2$
asymmetry and tail under-sampling on the small-$n$ side rather than
a real distribution mismatch — the raw sample mean and standard
deviation of our $n_1 = 500$ sub-sample are themselves outside their
respective bootstrap CIs at $|z| \approx 2.7$, while the
shape-robust skew-normal parameters are inside. The fit-parameter
bootstrap CI is therefore the operationally relevant
spectrum-validation criterion for this regime, and the Pt(Au)
spectrum passes.

\paragraph*{Pt(Au) downstream.}
The Pt(Au) HMC sampling on the $(T, X_c)$ grid analogous to
Sec.~\ref{sec:meth:grid} is in progress by the collaborator and will
populate the corresponding Results section once complete. The same
fdseed initial-condition methodology, Metropolis swap kinetics, and
trajectory bootstrap CI of Sec.~\ref{sec:meth:stats} carry over
unchanged from the Al(Mg) framework.

% =============================================================================
% End of patches.
% =============================================================================
